---
title: "A Decade of NIH Awards (2007-2017)"
output: html_notebook
---

Load the needed data files
```{r}
library(readr)

setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
data <- read_csv("data/2007-2017 - NIH Funding.csv")
data$FUNDING <- as.numeric(gsub('[$,]', '', data$FUNDING))
head(data)
```

Create a new dataset with missing data omited
```{r}
library(IDPmisc)
data_censored <- NaRV.omit(data)
```

```{r}
hist(data_censored$FUNDING/1e8, main = "2007-2017 - NIH Funding", xlab = "Millions $")
```

Look at log 10 Funding Distribution
```{r}
data_censored$FUNDING <- log(data_censored$FUNDING, 10)
head(data_censored)
avg <- mean(data_censored$FUNDING)
std <- sd(data_censored$FUNDING)
hist(data_censored$FUNDING, main = "2007-2017 - NIH Funding", xlab = "Log 10 ($)")
```

What're BCM values?
```{r}
dfBCM <- subset(data_censored, ORGANIZATION == "BAYLOR COLLEGE OF MEDICINE")
head(dfBCM)
```

```{r}
Look 

Add vertical lines for BCM
```{r}
hist(data_censored$FUNDING, main = "2007-2017 - NIH Funding", xlab = "Log 10 ($)")
lapply(dfBCM$FUNDING,
       FUN = function(award) {
         abline(v=award, col = "blue")
       })
```

Generate a time graph for BCM NIH finances
```{r}
## there's an issue where for years 2007-2010, BCM has two awards
plot(x=dfBCM$YEAR, y = dfBCM$FUNDING, xlab = "Year", ylab = "Log 10 ($)", main = "2007-2017 NIH Awards to Baylor College of Medicine")
```


